---
title: "Calories and Restaurants"
author: "Dan Fanelli"
date: "March 12, 2016"
output: html_document
---

### Calories and Restaurants (Jeffrey Nieman)

Found a fascinating source of data on calories and nutrients of going out to eat vs. not.  The link is http://www.ars.usda.gov/SP2UserFiles/Place/80400530/pdf/1112/Table_53_RST_GEN_11.pdf and just use the first page. 

Look at the caloric intake.

```{r message=FALSE, warning=FALSE}
library(dplyr)

# required cols will be: gender, age_group, Total intake kcal for restaurant consumers, Total intake kcal for non-consumers, Percentage from restaurant for restaurant consumers
df <- read.csv("calories and restaurants.csv", header = TRUE, sep = ",")

df <- df[ , which(names(df) %in% c("Gender","Age","Total.intake.kcal.for.restaurant.consumers","Total.intake.kcal.for.non.consumers","Percentage.from.restaurant.for.restaurant.consumers"))]

names(df) <- c('gender','age_group','eat_outs_total_kcal','eat_outs_rstrnt_pct','eat_ins_total_kcal')

df[c(2:6),'gender'] <- "Male"
df[c(8:12),'gender'] <- "Female"

df
```

#### Compare by gender and/or age groups the difference in calories for those who eat out vs. those who did not

```{r message=FALSE, warning=FALSE}
summarise(group_by(df, gender), eat_outs_avg_cal=mean(eat_outs_total_kcal), eat_ins_avg_cal=mean(eat_ins_total_kcal))

summarise(group_by(df, age_group), eat_outs_avg_cal=mean(eat_outs_total_kcal), eat_ins_avg_cal=mean(eat_ins_total_kcal))
```

#### Compare by gender and/or age groups the % of calories from restaurants for those who did eat out

```{r message=FALSE, warning=FALSE}
summarise(group_by(df, gender), eat_outs_rstrnt_cal_pct=mean(eat_outs_rstrnt_pct))

summarise(group_by(df, age_group), eat_outs_rstrnt_cal_pct=mean(eat_outs_rstrnt_pct))
```

___There was no column for "EAT INS RESTAURANT PCT" (unless I missed it...)___

