---
title: "Project 2 - DA 607"
author: "Dan Fanelli"
output: html_document
---

### Leading Causes of Death in NYC (Armenoush Aslanian-persico)


```{r message=FALSE, warning=FALSE}
library(dplyr)
library(knitr)

options(dplyr.width = Inf)
df <- read.csv("New_York_City_Leading_Causes_of_Death.csv", header=TRUE, sep=",")

kable(head(df))

```

## Analysis:

### 1. Show the leading causes of death each year for men and women.

```{r message=FALSE, warning=FALSE}
df1 <- df %>% subset(select = c(Sex,Year,Cause.of.Death,Count)) %>% 
  group_by(Sex,Year) %>%
  filter(Count == max(Count)) %>% distinct(Sex,Year,Cause.of.Death,Count)

kable(df1)

```

### 2. Show the leading causes of death each year for each ethnic group.

```{r message=FALSE, warning=FALSE}
df2 <- df %>% subset(select = c(Ethnicity,Year,Cause.of.Death,Count)) %>% 
  group_by(Ethnicity,Year) %>%
  filter(Count == max(Count)) %>% distinct(Ethnicity,Year,Cause.of.Death,Count)

kable(df2)
```

### 3. Calculate which cause of death has declined the most and which has increased the most in the years given.

```{r message=FALSE, warning=FALSE}
df_3 <- df %>% subset(select = c(Year,Cause.of.Death,Count)) %>%
  group_by(Year, Cause.of.Death, the_min = min(Count), the_max = max(Count), the_diff = (the_max - the_min)) %>% count(Year, Cause.of.Death, max(the_diff))

kable(df_3)
```

### 4. Calculate which cause of death has remained stable over the years given.

```{r message=FALSE, warning=FALSE}
df_4 <- df %>% subset(select = c(Year,Cause.of.Death,Count)) %>%
  group_by(Year, Cause.of.Death, the_min = min(Count), the_max = max(Count), the_diff = (the_max - the_min)) %>% count(Year, Cause.of.Death, min(the_diff))

kable(df_4)
```



