---
title: "DA607 Week 02 Assignment"
author: "Dan Fanelli"
date: "February 4, 2016"
output: html_document
---

Set your working directory to the same location as this Rmd file.

If you don't want to keep re-downloading the data files, put a # in front of the 2 download statements below:

```{r}
#download.file("https://archive.ics.uci.edu/ml/machine-learning-databases/housing/housing.data", "./housing.data")
#download.file("https://archive.ics.uci.edu/ml/machine-learning-databases/housing/housing.names", "./housing.names")
```

Read that file into a data frame and show its str and dim:

```{r}
initial.data.frame <- read.table("./housing.data", header=FALSE)

str(initial.data.frame)

dim(initial.data.frame)

```

The following came from the HEADER file, but we'll manually rename these to be more user friendly:

7. Attribute Information:

    1. CRIM      per capita crime rate by town
    2. ZN        proportion of residential land zoned for lots over 
                 25,000 sq.ft.
    3. INDUS     proportion of non-retail business acres per town
    4. CHAS      Charles River dummy variable (= 1 if tract bounds 
                 river; 0 otherwise)
    5. NOX       nitric oxides concentration (parts per 10 million)
    6. RM        average number of rooms per dwelling
    7. AGE       proportion of owner-occupied units built prior to 1940
    8. DIS       weighted distances to five Boston employment centres
    9. RAD       index of accessibility to radial highways
    10. TAX      full-value property-tax rate per $10,000
    11. PTRATIO  pupil-teacher ratio by town
    12. B        1000(Bk - 0.63)^2 where Bk is the proportion of blacks 
                 by town
    13. LSTAT    % lower status of the population
    14. MEDV     Median value of owner-occupied homes in $1000's

Now, lets set the col names exactly as they were in that header file:

```{r}
colnames(initial.data.frame) <- c("CRIM", "ZN", "INDUS", "CHAS", "NOX", "RM", "AGE", "DIS", "RAD", "TAX", "PTRATIO", "B", "LSTAT", "MEDV")

```

Now, lets subset the data by column name, and take the interesting ones:

```{r}
cols.subset.data.frame <- initial.data.frame[,c("CRIM","AGE","TAX","MEDV")]

head(cols.subset.data.frame)
```

Finally, lets only look at the "20-Somethings" crowd:

```{r}
rows.subset.data.frame <- cols.subset.data.frame[ which(cols.subset.data.frame$AGE>=20 & cols.subset.data.frame$AGE < 30), ]

head(rows.subset.data.frame)
```


The End.
