---
title: "DA607 Week 03 Assignment"
author: "Dan Fanelli"
date: "February 13, 2016"
output: pdf_document
---

#### Pre Reqs:
* The table: __tb__ was created using the script: https://raw.githubusercontent.com/fandang/DA607/master/Wk03/tb.sql
* The __tb__ table was loaded with data from the csv: https://raw.githubusercontent.com/fandang/DA607/master/Wk03/tb.csv
* The __population__ db table was loaded using __populations.csv__ (https://raw.githubusercontent.com/fandang/DA607/master/Wk03/population.csv)
* The 2 tables were tested with SQL to be sure that the countries (the join column) were in sync:

```sql
select count(country) from population where country not in (select country from tb)

select count(country) from tb where country not in (select country from population)
```

* The results for both came back __0__, so the tables join columns seem to be in sync.
* The following query was run against the DB:

```sql
select population.country, population.year, 
(IFNULL(tb.child, 0)+IFNULL(tb.adult, 0)+IFNULL(tb.elderly, 0)) as fatalities,
population.population, 
((IFNULL(tb.child, 0)+IFNULL(tb.adult, 0)+IFNULL(tb.elderly, 0))/population.population) as rate
from population, tb 
where population.country = tb.country and population.year = tb.year
group by population.country, population.year, population.population
order by rate desc
```

* The results of that query were exported to a csv and uploaded to: https://raw.githubusercontent.com/fandang/DA607/master/Wk03/joined_results.csv
* After that, the summary data was used to create a plot:


```{r message=FALSE, warning=FALSE}
library(ggplot2)

dataUrl <- "https://raw.githubusercontent.com/fandang/DA607/master/Wk03/joined_results.csv"
df <- read.csv(dataUrl, header = TRUE)
head(df)
```

Now, subset the data (pick a random few countries) to get an overall idea of the data, and plot it with GGPlot.

```{r message=FALSE, warning=FALSE}
subsetDF <- subset(df, country=='Swaziland'|country=='Bangladesh'|country=='South Africa'|country=='Guatemala'|country=='Turkey'|country=='Brazil'|country=='Spain')
  
ggplot(subsetDF,aes(x=year,y=rate,colour=country,group=country)) + geom_line()
```

