---
title: "DA607 Week 10 Assignment"
author: "Dan Fanelli"
date: "March 28, 2016"
output: pdf_document
---

# Assignment - Web APIs

The New York Times web site provides a rich set of APIs, as described here: http://developer.nytimes.com/docs

You'll need to start by signing up for an API key. (df956f71033315e19a189086a92e03b6%3A1%3A59370888)

Your task is to choose one of the New York Times APIs, construct an interface in R to read in the JSON data, and transform it to an R dataframe.


```{r message=FALSE, warning=FALSE}
library(jsonlite)
library(knitr)

# NY Times Congress API Key: df956f71033315e19a189086a92e03b6:1:59370888

NY_TIMES_CONGRESS_HOUSE_MEMBERS_JSON_URL = 'http://api.nytimes.com/svc/politics/v3/us/legislative/congress/102-113/house/members/current.json?api-key=df956f71033315e19a189086a92e03b6%3A1%3A59370888'

json_file <- fromJSON(NY_TIMES_CONGRESS_HOUSE_MEMBERS_JSON_URL)
df <- as.data.frame(json_file$results$members)
```

## The Following are a list of (the top 20) Members of Congress:

Subset with good UI:

```{r message=FALSE, warning=FALSE}
kable(head(df[ , (names(df) %in% c('id','first_name','last_name','state','party','seniority','missed_votes'))], n = 20))
```

All columns with core UI:

```{r message=FALSE, warning=FALSE}
head(df, n = 20)
```

