---
title: "Project 4 - DA 607"
author: "Dan Fanelli"
date: "April 16, 2016"
output: html_document
---

This project will load film and actor data from the sakila MySQL database and write the data to a Neo4J Database.

## Setup/Prereqs: 

* MySQL DB installed and running at
* MySQL create schema with script: sakila-schema.sql
* MySQL load data with script: sakila-data.sql

* Neo4j installed and running at: http://localhost:7474/db/data/

## Imports and Credentials: 

```{r warning=FALSE, message=FALSE}
library(RMySQL)
library(RNeo4j)
library(knitr)
library(igraph)
library(visNetwork)

DO_DEBUG = FALSE

NEO4J_GRAPH_URL <- 'http://localhost:7474/db/data/'
NEO4J_USER <- 'neo4j'
NEO4J_PW <- 'neo5j'

MYSQL_HOST <- '127.0.0.1'
MYSQL_USER <- 'root'
MYSQL_PW <- 'george'
MYSQL_SCHEMA <- 'sakila'
# to limit this query if it takes too long....
FILMS_LIMIT <- 200
```

## MySQL and Neo4J read/write/query functions: 

```{r warning=FALSE, message=FALSE}
# Get the MySQL DB
get_mysql_db <- function(film){
  the_db = dbConnect(MySQL(), user=MYSQL_USER, password=MYSQL_PW, dbname=MYSQL_SCHEMA, host=MYSQL_HOST)
  return (the_db)
}

# Create a GraphDB Film based on DB Row
create_neo4j_film <- function(film, db, graph, films_df){
  
  film_id <- film[1]
  film_title <- film[2]
  film_desc <- film[3]
  film_year <- film[4]
  if(DO_DEBUG)
    print(cat(film_id, '-', film_title, '-', film_desc, '-', film_year))
  
  the_film_node = createNode(graph, "Film", title=film_title, year=film_year, desc=film_desc)
  
    select_actors_sql <- paste0('select a.first_name, a.last_name from actor a, film_actor fa where a.actor_id = fa.actor_id and fa.film_id = ', film_id)
  rs = dbSendQuery(db, select_actors_sql)
  actors_df = fetch(rs, n=-1)
  if(DO_DEBUG)
    print(cat("film: ",film_title))
  apply(actors_df, 1, function(y) create_neo4j_actor_and_perf(y, db = the_db, graph = graph, film_node = the_film_node, film_title=film_title))
  if(DO_DEBUG)
    print("done with film.")
}

# Create a GraphDB Actor based on DB Row
create_neo4j_actor_and_perf <- function(actor, db, graph, film_node, film_title){
  actor_first_name <- actor[1]
  actor_last_name <- actor[2]
  the_actor_node = createNode(graph, "Actor", first_name=actor_first_name, last_name=actor_last_name)
  performance_rel = createRel(the_actor_node, "PERFORMANCE", film_node)
}

# Run the whole thing: DB Select, Graph Load
mysql_select_and_neo4j_load <- function(the_graph){
  the_mysql_db <- get_mysql_db()
  rs = dbSendQuery(the_mysql_db, paste0('select film_id, title, description, release_year from film limit ', FILMS_LIMIT))
  films_df = fetch(rs, n=-1)
  kable(head(films_df))
  print('db loaded and queried.')
  apply(films_df, 1, function(x) create_neo4j_film(x, db = the_mysql_db, graph = the_graph, films_df = films_df))
}

######## Select the data from mysql, and load it into neo4j:
the_graph = startGraph(NEO4J_GRAPH_URL, username=NEO4J_USER, password=NEO4J_PW)

mysql_select_and_neo4j_load(the_graph)
print('Done with mysql select and neo4j load.')
```

## Now prove the Neo4J Data store got loaded with some queries: 

### QUERY: Find ACADEMY DINOSAUR

```{r warning=FALSE, message=FALSE}
cypherToList(the_graph, "MATCH (found_flic {title: 'ACADEMY DINOSAUR'}) RETURN found_flic.title, found_flic.year")
```

### QUERY: Actors with last name BLOOM

```{r warning=FALSE, message=FALSE}
cypherToList(the_graph, "MATCH (found_actor {last_name: 'BLOOM'}) RETURN found_actor.first_name, found_actor.last_name")
```

### QUERY: Actors with first name JOHN

```{r warning=FALSE, message=FALSE}
cypherToList(the_graph, "MATCH (found_actor {first_name: 'JOHN'}) RETURN found_actor.first_name, found_actor.last_name")
```


